\documentclass[a4paper,9pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage[left=2cm, right=2cm, top=2.5cm, bottom=2.5cm]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

\pagestyle{empty}

\centerline{\huge \textbf{Hadrien Cornier}}

\vspace{2mm}

\centerline{Austin, Texas, United States | \href{mailto:hadrien.cornier@gmail.com}{hadrien.cornier@gmail.com} | \href{https://linkedin.com/in/hadrien-cornier}{linkedin.com/in/hadrien-cornier}}

\vspace{4mm}

\noindent\textit{Curious technologist driven to leverage AI for real-world impact. I've had the privilege of working on hardcore ML at several innovative startups. At Talroo, I'm tackling the complex problem of sponsored job matching, surrounded by brilliant colleagues all contributing to our mission. It's a place where you'll develop deep expertise while shaping the future of recruiting. If you're passionate about learning and building the whole stack of AI of a marketplace and search backend and make a difference, Talroo is where it's at. Let's chat!}

\vspace{4mm}

\section*{Experience}

\noindent\textbf{Senior ML Engineer}, Talroo, \textit{Austin, TX} \hfill Oct 2022 - Present\\
Leading the gen ai team. Before that : Improving rankings and decreasing latency \& cost per query through research and engineering. Designed end-to-end overhaul to our search system boosting revenue by 20\%. Introduced a system that increased CPC long term by 30\%.\\    

\noindent\textbf{ML Engineer}, Talroo, \textit{Austin, TX} \hfill Jul 2021 - Oct 2022\\
    Worked on the AI behind Talroo powering hundreds of job boards in the US. Delivered millions in savings by decreasing latency by 25\% and computational cost by 7x. Merged the dual inference strategy into a single system improving CTR by 15\%.\\

    \noindent\textbf{ML Engineer}, Augustus Intelligence, \textit{New York City} \hfill Apr 2020 - Jul 2021\\
    R\&D for a Bayesian computer vision pipeline for visual industrial anomaly detection. Engineered full redesign for the control system of a network of thousands of sensors.\\

    \noindent\textbf{Machine Learning Intern}, Revelio Labs, \textit{New York City} \hfill Jun 2019 - Aug 2019\\
    Designed and deployed 2 models for company payroll estimation and resume value generating \$150k in revenue. Decreased the average error rate by 50\% through tuning.\\

    \noindent\textbf{Summer Research Intern}, Atos, \textit{Les Clayes-sous-Bois, France} \hfill Apr 2017 - Sep 2017\\
    Wrote a Haskell translator of Quipper into aQasm for the research team working on the Atos QLM.\\

    \noindent\textbf{Officer Cadet}, Gendarmerie Nationale, \textit{Ajaccio, Corsica} \hfill Sep 2015 - Apr 2016\\
    Assisted the regional commander with a report on the mafia.

    \section*{Education}

    \noindent\textbf{Columbia University}, \textit{New York City} \hfill 2018 - 2019\\
    Master of Science - MS, Data Science\\

    \noindent\textbf{École Polytechnique}, \textit{Palaiseau, France} \hfill 2015 - 2019\\
    Master of Science - MS, Computer Science and Applied Mathematics\\

    \noindent\textbf{Collège Stanislas Paris}, \textit{Paris, France} \hfill 2013 - 2015\\
    Bachelor of Science - BS, Mathematics, Physics, Computer Science, Electrical \& Mechanical Engineering\\
    Classes préparatoires scientifiques (MPSI - PSI*)\\

    \noindent\textbf{Collège Stanislas Paris}, \textit{Paris, France} \hfill 2008 - 2013\\
    Scientific Baccalauréat - Option Mathematics\\

    \section*{Skills}
    Machine Learning, Python, Research and Development (R\&D), Data Engineering, Machine Learning Infrastructure Optimization, Embedded Systems, Early-Stage Startups

\end{document}
